Efficient Handling of String-Number Conversion

### 2020-04-05 final-final/main.tex
final version

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\acmPrice{}
\acmDOI{10.1145/3385412.3386034}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{pldi20main-p869-p}
\acmISBN{978-1-4503-7613-6/20/06}
\acmConference[PLDI '20]{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 15--20, 2020}{London, UK}
\acmBooktitle{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '20), June 15--20, 2020, London, UK}

@@

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. \changed{However, solving this type of constraint is very challenging for the state-of-the-art solvers. 
We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.} Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\acmPrice{15.00}
\acmDOI{10.1145/3385412.3386034}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{pldi20main-p869-p}
\acmISBN{978-1-4503-7613-6/20/06}
\acmConference[PLDI '20]{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 15--20, 2020}{London, UK}
\acmBooktitle{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '20), June 15--20, 2020, London, UK}

@@

\begin{abstract}
String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. However, solving this type of constraint is very challenging for the state-of-the-art solvers. 
We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}
